A new tidy data structure to support exploration and modeling of temporal data

### 2019-01-28 main.Rmd
more in acknowledgements #3

The authors thank Mitchell O'Hara-Wild for many discussions on the software design.

```{r write-bib}
write_bib(c("dplyr", "tidyr", "purrr", "nanotime", "tibbletime", "tsibble", "knitr", "rmarkdown"), file = "rpkgs.bib")
```

>>>>

The authors would like to thank Mitchell O'Hara-Wild for many discussions on the software development and Davis Vaughan for contributing ideas on rolling window functions. This article was created with knitr [@knitr] and R Markdown [@rmarkdown]. The project's Github repository <https://github.com/earowang/paper-tsibble> houses all materials required to reproduce this article and a history of the changes. To produce the analysis results as described in Section \autoref{sec:cases}, we require the **tsibble** package (`v0.6.2`) and the **dplyr** package (`v0.7.8`) installed.

```{r write-bib}
write_bib(c("dplyr", "tidyr", "purrr", "nanotime", "tibbletime", "tsibble"), file = "rpkgs.bib")
```
